% Chapter 2: The Office
% Scene function: Break room, the New Hire, the Apparitions hallway,
% transit to Earth. Establishes the office as a social world and the
% New Hire as a character. Ends on arrival at the house.

\chapter{Hat}

I stop at the break room on my way back from Intake. The coffee is the wrong temperature. It is always the wrong temperature. Not hot, not cold. Not lukewarm in the way that implies it was once hot and cooled. Lukewarm in a way that suggests it was manufactured at this exact temperature specifically to disappoint. I drink it anyway.

The new hire is in the break room. I know they are the new hire because they are sitting at a table with a copy of the Operations Manual open in front of them, which means they are either on their first week or they have been written up for a protocol violation and are being punished with the required corrective reading. Nobody else opens the Operations Manual voluntarily. I took mine out of the shrink-wrap in 2004 to look up whether I could expense a particular type of chalk. I could not. I have not opened it since.

``Excuse me,'' the new hire says. ``Can I ask you something?''

This is a question I have learned to be cautious with. The things new hires want to ask range from procedurally answerable (``where is the transit desk?'') to philosophically catastrophic (``what is the actual mechanism by which fear produces a harvestable soul?''). There is no way to tell which kind you are getting until you have already said yes.

``Depends,'' I say.

``Why do we do the flickering lights thing?''

I sip my coffee. It is exactly the temperature I expect.

``Flickering disrupts the visual baseline,'' I say. ``Humans process environmental continuity as a safety signal. When a light source stutters, even briefly, the visual cortex flags it before the conscious mind can decide whether to worry. That is your opening. You are not scaring them with the flicker. You are telling their nervous system that the environment is unstable. The fear comes later, from what they do with that information.''

The new hire nods. She has a pen out. She is taking notes in the margins of the Operations Manual.

``But what does that do for the pipeline?'' she says. ``Like, how does making a light flicker lead to a harvestable soul?''

There it is. The pivot from procedurally answerable to philosophically catastrophic, right where I said it would be, and I walked into it anyway.

``That is above my operational scope,'' I say, which is the phrase Management uses when they do not want to answer a question. I have picked it up the way people pick up phrases from the organization they work in, without deciding to and without being proud of it.

The new hire writes this down too. I watch her write it. She writes it in the margin next to a paragraph that presumably already contains the official answer, which means either she has read the official answer and found it insufficient, or she has not read it yet and is collecting opinions first. I do not know which is worse.

``What about salt?'' she says.

``It is fine on eggs,'' I say. ``Overused in most other contexts.''

She looks at me. I sip my coffee.

``Holy water?''

``Depends on who blessed it. Nobody knows why. Controlled studies have been proposed. HR rejected them.''

``Crucifixes?''

``Mildly irritating at close range. Like a bright light. Older ones are worse. Nobody knows why that either.''

``Sage?''

``The smoke is unpleasant. So is all smoke. The humans who burn it tend to open windows, which affects air currents, which can interfere with thermal work. The window is the problem, not the sage.''

``Iron?''

I pause. ``Iron is uncomfortable. Route around it.''

``So iron actually works.''

``Iron is uncomfortable,'' I say. ``I did not say it works. I said I route around it. I also route around traffic and dogs.''

``Dogs?''

``Dogs notice you. They do not care. They look at you and go back to sleep. Junior operatives find this unnerving. It is not a countermeasure. It is a dog.''

She is writing very quickly.

``What is your name?'' I say.

``Eighth Meridian,'' she says. ``Atmospheric Hauntings, Operative 112-F. People have been calling me Meri.''

``They would,'' I say.

I finish my coffee and put the cup in the designated area, which is a counter next to a sink that nobody has ever seen running water come out of. The cups accumulate there until they do not, which implies someone or something collects them, but I have never witnessed this and I am not curious enough to investigate.

I take the lower corridor toward transit. It is longer today than it was yesterday. This happens. Somewhere between the break room and the stairwell, I pass someone from Apparitions. I know they are from Apparitions because they are adjusting their face in the hallway mirror. Apparitions operatives spend a lot of time on their faces. They have a whole department workshop on it: ``Facial Presentation for Maximum Startle.'' I attended it once, by accident, having misread a room number. The content was exactly what you would expect from a department that believes the key to damnation is making the right expression at the right moment. There were slides. There was a ranking system. Someone had strong opinions about whether the eyes or the mouth delivers more impact per millisecond of exposure. I left during a debate about jawlines.

The operative in the mirror catches my eye and nods. I nod back. We do not understand each other's work, but the nod costs nothing.

The transit desk is at the end of the lower corridor, behind a door marked 1-14B. The desk itself is unoccupied. There is a sign-out clipboard on a chain bolted to the wall, a stack of transit forms in a plastic tray, and a second door on the far side of the room, also marked 1-14B, which would be confusing if you thought about it, so I do not.

I fill in a transit form. Name, designation, case number, destination address, estimated shift duration, expected return. The form has not been updated since at least the 1990s. There is a field for ``mode of concealment (circle one):'' followed by options that include ``spectral translucency,'' ``environmental camouflage,'' and ``hat.'' I circle hat.

I slide the form through the slot. I open the far door.

The house is at the end of a quiet street in an old grid neighborhood, and I am standing on the sidewalk across from it in late-afternoon light. The maple in the front yard is not bare now. It has leaves. Spring has arrived since the survey photographs were taken. The house is exactly the color between gray and green. The swing on the front porch moves slightly in the wind.

I do not go in yet. The first visit is observation. You do not begin a haunting by doing something. You begin it by learning where you are.
