% Chapter 6: Week Two
% Scene function: The haunting becomes specific. First manipulated
% creak pays off ch4's setup. Gordon starts noticing things and
% attributing them to grief. Tert starts thinking of him as Gordon.

\chapter{Six Minutes Early}

On Thursday night, I make the first joist creak six minutes early.

I am in the basement with my hand on the beam under the bookshelf wall. I have spent three nights learning its rhythm. At 1:47 a.m., the joist would ordinarily release its next stress event: a low creak that travels through the floor and arrives in the living room and the hallway and the bedroom at slightly different times. The subject has heard this sound every night for twenty years. His body knows when it is coming even if his mind does not.

At 1:41, I apply pressure to the bearing point. Not much. Enough to accelerate the contraction by six minutes. The stress releases. The creak arrives.

It is the same creak. Same frequency, same resonance, same arrival pattern. Nothing about the sound itself is wrong. What is wrong is the timing. The discrepancy is below conscious threshold, but the body keeps its own schedule, and when the schedule is off, the body notices.

From the bedroom, I hear Gordon shift in his sleep. Not wake. Shift. One position adjustment, the kind that happens when the autonomic nervous system receives information it cannot act on and translates it into movement.

I do this three more times before dawn, each on a different joist, each shifted by a different interval. I will see the result in his posture by Friday, in the specific way a person carries themselves when they have slept for eight hours and rested for six.

On Friday night, I run the bathroom tap for two seconds while Gordon is in the hallway. Not long enough to be certain. Just long enough to register from six feet away, where he is walking past the bathroom on his way to bed. He pauses. Two seconds is below the threshold of certainty. Was the tap on? Is the handle loose? He does not open the bathroom door. He continues to the bedroom. But he paused. A pause is all I need.

I have started thinking of him as Gordon, which the Operations Manual advises against. The Operations Manual has not spent ten days in his house.

On Saturday I introduce a low-frequency vibration in the water pipes, timed to coincide with the house's thermal settling, so that the pipes and the joists produce overlapping sounds that Gordon's nervous system cannot separate. The house no longer has a clean rhythm. It has a complex one, and complexity reads as instability.

On Sunday evening Gordon is sitting in his armchair reading. Not aloud. A different book. He reads a page, sets it down, picks it up again. He cannot concentrate. He stands up and checks the thermostat. It reads sixty-six. He looks at it for a moment. He turns it up to sixty-eight.

He found the thermostat. I will not use it again.

He goes back to his chair. He picks up the book. He reads the same page. After a few minutes he puts it down and goes to the kitchen to make tea. He brings the tea back to the living room. He does not drink it.

I am satisfied with the work.
