% Chapter 7: The Garden
% Scene function: Gordon tends his dead wife's garden. Tert watches.
% The shortest chapter so far. Every sentence carries weight.
% The margin-pad note at the end is the gap made visible.

\chapter{The Garden}

On Tuesday, Gordon goes into the garden.

I was not expecting this. His pattern has been consistent: leave by nine, return by four. Today he does not leave. He eats breakfast, washes the dishes, and stands in the kitchen for a long time looking out the window at the back yard.

The garden is along the back fence. His wife's. I can tell because the structure is intentional: raised beds, a trellis, a stone border. But the maintenance has been nothing for ten months. The beds are overgrown. The trellis has collapsed on one side.

Gordon goes outside and stands at the edge of the garden the way I stood in the living room on my first visit: reading the space, assessing what is here and what could be done with it.

He starts pulling weeds. He does not appear to know what is a weed and what is not. He pulls several things I suspect were planted on purpose. He works for about forty minutes. The raised bed does not look better when he is done. It looks different, which is not the same thing, but he regards it as if it is.

He goes inside, eats lunch standing at the counter, looking out the window at the bed.

He goes back out and works for another hour. He finds the collapsed trellis and tries to fix it. He does not have the right tools or the right knowledge. He props it against the fence in a configuration that will not survive a moderate wind. He steps back. He adjusts one side. He steps back again.

I make a note in my margin pad: \emph{subject engaging with outdoor space; investigate external sound vectors.}
