% Chapter 13b: Two Cups
% Scene function: Gordon invites someone over. His world is not
% shrinking. It is rebuilding. The system's model is wrong.
% Tert watches from the hallway. No margin pad note.

\chapter{Two Cups}

On Saturday afternoon, Gordon calls the woman from the dinner invitation.

I am in the hallway. He is in the kitchen. He dials the number from memory, which means he has called it before, many times, over many years.

``Helen,'' he says. ``Are you free tomorrow? I thought you might like to come for tea.''

She says yes. He says two o'clock. He hangs up and stands in the kitchen for a moment, and then he does something I have not seen him do in four weeks of observation: he cleans the living room.

Not because it is dirty. Because someone is coming. He straightens the books on the coffee table. He washes the mug that has been drying on the counter and puts it away. He takes out a second mug. He puts a kettle on the stove to test whether it still works. It does. He puts it back.

Sunday at two, Helen arrives. She is roughly Gordon's age. She brings something in a container. They sit in the living room, in the two armchairs, and they talk.

I am in the hallway. I cannot hear the conversation clearly. I can hear the quality of Gordon's voice, and it is the voice from the readings: warm, unhurried, shaped for someone else's benefit. Helen's voice is similar. They are two people who have known each other for a long time sitting in a room full of books having a conversation that does not need to be loud.

She stays for an hour. When she leaves, Gordon walks her to the door. He says something I cannot hear. She laughs. He closes the door and goes to the kitchen and washes the cups. Two cups.

He puts them both away.
