% Chapter 13: Mid-Cycle
% Scene function: Prim's mid-cycle review. Prim notices the delayed
% follow-up intervals. Asks the right question in the wrong language.
% Gets exactly the answer the form was designed to produce.

\chapter{Mid-Cycle}

Prim schedules the mid-cycle review for Thursday.

I know it is a mid-cycle review because it is on the calendar as ``Mid-Cycle Performance Assessment (Field),'' and because it takes place in a room with a door, which the week-one check-in did not. The room has a table, two chairs, and a motivational poster that says EXCELLENCE IS A HABIT. Nobody has removed the poster. Nobody enters this room voluntarily.

``Tert,'' Prim says, sitting down with the clipboard. The clipboard has more pages than it did during the week-one check-in. They have tabbed the sections. ``Thank you for coming in.''

I was not given a choice about coming in, but I say ``of course'' because this is the script and deviating from the script would add time without adding clarity.

``I have been reviewing your shift reports for forty-seven-C. Weeks one through four.'' Prim opens the clipboard to a tabbed section. ``The numbers look strong. Timeline adherence is at ninety-two percent. Fear Index progression is on curve. Collateral Awareness is well below threshold.''

``Good,'' I say, because this is where Prim pauses and expects a response, and ``good'' is the one that lets them continue.

``I am noticing a pattern in your follow-up intervals, though. Weeks three and four, you have several entries where the secondary event was delayed. Thermal conditions, mostly.'' Prim looks up from the clipboard. ``Is there an environmental factor I should flag for Intake? Something about the dwelling's thermal profile that is affecting your layering schedule?''

Prim noticed. Prim reads the forms and Prim noticed that my follow-up intervals changed after week two. This is what careful reading does. This is what I was concerned about when Prim read my week-three modification, and it is exactly as uncomfortable now as it was then, and for different reasons.

``The house has complex thermal behavior,'' I say. ``Original construction, plaster walls, uneven insulation. Some nights the conditions are not optimal for layered events.''

This is true. Every word of it is true. None of these facts is the reason my follow-up intervals changed, and all of them are sufficient to satisfy the field on the form.

Prim writes this down. ``I will note it as an environmental variable. If it persists into week five, we may want Intake to do a supplemental thermal survey.''

A supplemental thermal survey of a house I have mapped to the individual joist. But the process recommends a survey, and so a survey will be recommended.

``That would be fine,'' I say.

``One more thing. The Soul Outcome projection. We are still tracking seventy-two percent. Any movement?''

The seventy-two percent was never attached to anything that moves.

``I will have a clearer picture by case closure,'' I say.

``Good.'' Prim closes the clipboard. ``The work looks solid, Tert. Keep it up.''

They leave. Prim noticed the pattern and asked the right question in the wrong language. The form gave them the only answer it had.
