% Chapter 14c: Please Address
% Scene function: A Post-it from Prim. The mirror wasn't enough.
% The system demands a second direct-perception event.

\chapter{Please Address}

There is a note on my desk. A Post-it. Informal. Not documented. From Prim.

It says: \emph{47-C Phase 4: checklist shows one direct-perception event this week. Minimum is two. Please address before week close.}

I read it twice. The handwriting is steady and small. Several hundred demons, one consistent hand.

``Please address'' is Prim's way of leaving a gap in the form without making the gap official. If I address it, the gap was never there. If I do not, the next note will not be on a Post-it.

I put the note in my desk drawer. Four weeks of the most precise atmospheric work I have ever done, and I still owe the checklist a party trick.

I get coffee. It is the wrong temperature. I take it back to my desk and open a blank planning sheet.

A direct-perception event. Subject must achieve visual contact with the operative for a minimum of three seconds. Any positioning, any light condition, any angle. I write ``doorway'' on the planning sheet. I cross it out. I write ``hallway (backlit).'' I cross it out. I write ``doorway'' again.

I consider requesting a consult with Apparitions. They have office hours for this. The sign-up sheet is on the board next to the break room. I have walked past it for years. I would rather file a thermal survey on a house I have already mapped to the individual joist.

Meri passes my desk. She glances at the planning sheet.

``Doorway,'' she reads.

``Yes.''

``You crossed it out.''

``Yes.''

``Then you wrote it again.''

``Thank you, Meri.''

She keeps walking. Doorway it is.
