% Chapter 20: Completion
% Scene function: The last shift. Week 5 passive observation.
% Tert's accumulated knowledge of the house rendered as inventory.
% Gordon reads one last time. The string holds.

\chapter{Completion}

The protocol for week five specifies a final observation period. Twenty-four hours of passive monitoring to assess the subject's behavioral state at case closure. No interventions. No escalations. The operative is present but not active. The official purpose is to establish a closing baseline against which the Soul Outcome can be measured.

I have never understood what a closing baseline measures that the previous four weeks of shift reports do not already contain. But the protocol specifies it, and Prim will expect the documentation, and the form has a field for it.

Sunday evening. My last shift in this house.

The garden looks different from the first time I saw it. Not better, exactly. Attended. The raised bed has been weeded again, more carefully than before. The trellis is still propped against the fence in a configuration that will not survive winter, but someone has tied it with string. The string is new.

Inside, the house is the same house. The bookshelves. The fireplace. The armchairs, one facing slightly away from the other. The grab bar in the hallway. The sickroom door, closed. The empty nail above the mantel.

I have been in this house for thirty-five days. I know it better than any house I have worked in. I know which floorboard creaks at what temperature. I know where the streetlight falls through the living room window at two in the morning. I know the bathroom tap drips once every forty minutes when the water pressure drops, and that the kitchen refrigerator cycles on for eleven minutes and off for seven. I know the cast-iron radiator in the living room is the only object in this house that has ever caused me discomfort, and that Gordon turns it on when he gets cold. The most effective countermeasure in the house is the heating system, and it is not even trying.

I know that Gordon eats dinner at seven and watches television until nine-thirty and brushes his teeth at eleven and reads in bed for twenty minutes before turning off the light. I know he takes his coffee with milk and no sugar, and that he stirs it longer than he needs to. I know that he walks past the sickroom door without pausing, except once, when he opened it, and stood in the doorway for a long time, and closed it gently.

I know that on Sunday evenings he takes a book from the third shelf and reads aloud for about forty minutes in a voice that is not for the room.

He does this tonight. I listen from the hallway. The bookmark has moved since last week.

His voice carries through the house the way it always does: warm, unhurried, shaped for someone who is not here. I do not usually listen to the words. Tonight I hear them.

``If we had a keen vision and feeling of all ordinary human life, it would be like hearing the grass grow and the squirrel's heart beat, and we should die of that roar which lies on the other side of silence.''

He pauses. He turns the page.

He finishes. He puts the bookmark back. He places the book flat on the shelf. He turns off the lamp. He goes to bed.

I let myself out the back door.

The garden is dark. The trellis is a shape against the fence. The string holds.
