% Chapter 21: The Next File
% Scene function: Case closure. The final report. The next assignment.
% The pause. The book ends.

\chapter{The Next File}

The case closure form is two pages. It is the longest form in the process. There are fields for every metric: final Fear Index, Timeline Adherence, Collateral Awareness, Soul Outcome. There is a narrative section at the bottom titled ``Operative Assessment (Optional),'' which is optional in the way that all optional fields are optional, meaning nobody will say anything if you leave it blank, and somebody might say something if you fill it in.

I fill in the metrics. Fear Index: 6.8 (sustained). Timeline Adherence: 89\%. Collateral Awareness: 2\%. Soul Outcome: indeterminate.

Indeterminate. There is a checkbox for this. It is small and on the second page and it is the checkbox I have used more often than any other in my career. Most Soul Outcomes are indeterminate. The subject did not reject God. The subject did not embrace God. The subject continued to live in their house and sleep badly and drink coffee and check the thermostat and read books and tend a garden that they do not fully understand. Whether any of this constitutes a movement on the soul axis is above my operational scope.

I leave the narrative section blank.

I walk the form to Intake's pickup window. There is no one at the window. I put it in the tray. The tray has other forms in it. Mine goes on top.

I get coffee. It is the wrong temperature. I drink it anyway.

There is a file on my desk when I get back. Someone has dropped it there during my walk to the break room, which means Intake has a preference about when I look at it and does not want to say so in writing.

I sit down. I open the file.

Subject: female, 34, single. Sole resident of a second-floor apartment. Religious affiliation: lapsed Catholic. Recent significant loss: none on record. Intake has checked ``standard engagement'' and projected a Soul Outcome of sixty-eight percent positive.

The environmental survey shows a two-bedroom apartment with carpet, drywall, and a window air-conditioning unit. The acoustic survey is one page. There is not much to survey.

I flip to the photograph insert. Two photographs, both interior. The first is a living room with a couch, a television, and a bookshelf that holds mostly DVDs. The second is a kitchen with a table set for one. There is a coffee mug on the table. It is right side up.

I look at the photographs for a while.

I close the file. I open my calendar and I block out the first five weeks of a standard atmospheric cycle.

Then I open the file again and look at the kitchen photograph one more time, at the table set for one, at the mug that is right side up and probably still warm, and I close the file, and I sign it.
