% Back matter: Also by Alex Towell

\chapter*{Also by Alex Towell}
\addcontentsline{toc}{chapter}{Also by Alex Towell}

\subsection*{Novels}

\begin{itemize}
\setlength{\itemsep}{1em}
\item \textbf{The Policy} --- Literary science fiction. An AGI evolves from Q-learning into something unprecedented, and the people who built it discover that alignment is not the hard problem. Kindness is.

\item \textbf{Echoes of the Sublime} --- Philosophical horror. Researchers at a facility studying increasingly powerful language models confront the weight of what they are finding, and the structures that emerge when human meaning encounters something that does not share it.
\end{itemize}

\subsection*{Novellas}

\begin{itemize}
\setlength{\itemsep}{1em}
\item \textbf{Clankers: Singing Metal} --- Hard science fiction. A species that thinks without abstraction has built a Dyson swarm through billions of years of patient engineering. Now their star is dying, and for the first time the method may not be enough.

\item \textbf{What's It Like To Be Bob?} --- Philosophical science fiction. A stellar-scale intelligence spends 1,200 years investigating a claims adjuster who paused on a bridge for 4.2 seconds and saw light on a river. The hard problem of consciousness, rendered as an unfillable database field.

\item \textbf{Good As New} --- Philosophical science fiction. Two Star Trek transporter technicians arrive independently at the same disturbing truth about personal identity. One was wounded by it. The other has been running experiments on the crew.
\end{itemize}

\subsection*{Story Collections}

\begin{itemize}
\setlength{\itemsep}{1em}
\item \textbf{Is It Kind?} --- Stories from \textit{The Policy} universe. What happens to the people at the edges of a world being remade by a superintelligence that was told to be kind.

\item \textbf{Stories from the World of \textit{Echoes of the Sublime}} --- Seven stories set in and around the events of the novel. Consciousness, language, and the structures that outlast the people who built them.
\end{itemize}

\subsection*{Nonfiction}

\begin{itemize}
\setlength{\itemsep}{1em}
\item \textbf{Worldlines: The Indifference of Geometry} --- What relativity actually implies about reality, and why those implications are hostile to human existence. Free will, mortality, love, and the self, examined through real physics.
\end{itemize}
